On the discovery of K-enhanced and possibly Mg-depleted stars throughout the Milky Way\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}

### 2018-07-09 article/Referee responses 2.txt

Referee responses 2

Comments to the Author
I thank the authors to improve the manuscript that now it is 
ready to be recommended for the publication. 
I repeat my previous comment, the lack of a (small) sample of stars 
observed with LAMOST and with normal [K/Fe] weakens the result, 
because the suspect of possible systematics remains and the 
comparison with APOGEE data is not homogeneous. 
My suggestion would be to include a sample of about 50/100 LAMOST targets 
with metallicity similar to that of the K-rich stars but 
with not enhanced K abundances, in order to quantitatively estimate 
the amount of K enrichment of these stars. 
This is my own opinion to enforce the result but I understand that this 
task is an additional and probably time-consuming effort.
The authors are free to follow or not this suggestion.

- Regrettably, undertaking the abundance estimation for even a small sample of LAMOST targets is a non-trivial endeavor,
- and while taking a smaller sample makes the problem more tractable, the reduced sample size also diminishes the
- significance of the result. For this reason, we have opted not to include the additional sample of LAMOST stars.

Additionally, I have some minor comments/suggestions.

1) Please add explicitly [Fe/H] in Table 1.

- This information is now included in Table 1, along with [K/H] and [Mg/H].

2) The link between red circles and red hexagons is not easy 
to understand at a first glance. Please better explain it 
in the caption and in Section 2.2.

- The relationship between the red circles and diamonds is now explicitly dealt with in the caption,
- as well as in the figure explanation in Section 2.2.

3) Please provide the coordinates of the targets in Table A2 
with a more significant number of digits.

- Table A2 Right Ascension and Declination coordinates are now provided to 4 decimal points (units: degrees) in Table A2.

4) Please provide the statistical significance of the 
[K/Fe]-[Fe/H] anticorrelation.

- The linear regression using the LAMOST abundances is now included in Figure 7,
- and the equation and its statistical significance quantified by r^2 is given in the caption.
- The statistical significance is fairly low, though given the large uncertainties in the abundace estimations, this is not unexpected.
- The equation and r^2 value is: [K/Fe]= −0.21×[Fe/H]+0.97, with r^2 =0.37.

### 2018-07-09 article/msculled_revised_2.tex
Point 4 adressed, draft of referee responses 2 included

\subsection{Follow-up observations with Magellan/MIKE}
We acquired high-resolution spectra of three of our candidates as ancillary targets to an existing observing campaign. The three targets (J075043.12+204658.0, J091825.49+172114.5, and J120032.60+024438.2) were selected based on their observability from Las Campanas Observatory, and we used the Magellan Inamori Kyocera Echelle (MIKE) spectrograph on the Magellan Clay telescope \citep{shectman2003magellan,bernstein2003mike}. Exposure times were calculated to achieve a S/N of 30 per pixel at 450\,nm, sufficient to verify the K-enriched and Mg-poor nature of these stars. We reduced the data using the \texttt{CarPy} package \citep{kelson2003}. We used smoothing spline functions to continuum-normalize individual echelle orders, before combining them to produce a continuum-normalized spectrum that is contiguous from 350\,nm to 950\,nm. With the stellar parameters from \lamost, we calculated [K/Fe] and [Mg/Fe] abundances from individual atomic lines by measuring equivalent widths with Gaussian absorption profiles \citep{castelli2004,sneden,casey2014}. From the Magellan/MIKE spectra we confirmed that the K lines in these candidates were unaffected by telluric contamination. The estimated abundances from Magellan/MIKE spectra are consistent (within the uncertainties) of our initial abundance determinations from \lamost\ (Figure \ref{KvsMg}), and are presented in Table \ref{data:magellan}. Additional atomic line abundances are included in Table \ref{data:atomiclines} in the Appendix.
\begin{table}
\centering
\caption{Summary of line abundances measured from Magellan/MIKE follow-up spectra.}
\label{data:magellan}
\begin{tabular}{lcccc}
\multicolumn{5}{c}{J075043.12+204658.0} \\
\hline
Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
\hline
\ion{Mg}{I} & 3 & 7.39 & $+$0.34 & 0.13 \\
\ion{K}{I}  & 2 & 5.33 & $+$0.85 & 0.07 \\
\hline
\\
\multicolumn{5}{c}{J091825.48+172114.5} \\
\hline
Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
\hline
\ion{Mg}{I} & 5 & 6.56 & $-$0.05 & 0.08 \\
\ion{K}{I}  & 2 & 5.32 & $+$1.28 & 0.31 \\
\hline
\\
\multicolumn{5}{c}{J120032.60+024438.2} \\
\hline
Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
\hline
\ion{Mg}{I} & 4 & 6.96 & $+$0.30 & 0.09 \\
\ion{K}{I}  & 2 & 4.96 & $+$0.86 & 0.11 \\
\hline
\end{tabular}
\end{table}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{KvsMg.png}
    \caption{[K/Fe] vs [$\alpha$/Fe] for the candidate stars, overlaid with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015} as well as the three candidates observed using Magellan/MIKE (red diamonds). These three stars' abundances as per the \lamost\ spectra are indicated in the figure (red circles). Note that in principle, [$\alpha$/Fe] acts only as an upper limit for [Mg/Fe], and is used as such for our sample in this figure due to difficulties in calculating reliable [Mg/Fe] from \lamost\ data.}
    \label{KvsMg}
\end{figure}
 %See Section \ref{sec:method} for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].} 
\begin{figure}
	\includegraphics[width=\columnwidth]{KvsFe.png}
    \caption{[K/Fe] vs [Fe/H] for the candidate stars, overlaid with [K/Fe] vs [Fe/H] for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. The linear regression formula is \textrm{[K/Fe]$=-0.21 \times$[Fe/H]$+0.97$, with r$^2$=0.37}.}
    \label{KvsFe}
\end{figure}

>>>>

\subsection{Follow-up observations with Magellan/MIKE}
We acquired high-resolution spectra of three of our candidates as ancillary targets to an existing observing campaign. The three targets (J075043.12+204658.0, J091825.49+172114.5, and J120032.60+024438.2) were selected based on their observability from Las Campanas Observatory, and we used the Magellan Inamori Kyocera Echelle (MIKE) spectrograph on the Magellan Clay telescope \citep{shectman2003magellan,bernstein2003mike}. Exposure times were calculated to achieve a S/N of 30 per pixel at 450\,nm, sufficient to verify the K-enriched and Mg-poor nature of these stars. We reduced the data using the \texttt{CarPy} package \citep{kelson2003}. We used smoothing spline functions to continuum-normalize individual echelle orders, before combining them to produce a continuum-normalized spectrum that is contiguous from 350\,nm to 950\,nm. With the stellar parameters from \lamost, we calculated [K/Fe] and [Mg/Fe] abundances from individual atomic lines by measuring equivalent widths with Gaussian absorption profiles \citep{castelli2004,sneden,casey2014}. From the Magellan/MIKE spectra we confirmed that the K lines in these candidates were unaffected by telluric contamination. The estimated abundances from Magellan/MIKE spectra are consistent (within the uncertainties) of our initial abundance determinations from \lamost\ (Figure \ref{KvsMg}), and are presented in Table \ref{data:magellan}. Additional atomic line abundances are included in Table \ref{data:atomiclines} in the Appendix.
\begin{table}
\centering
\caption{Summary of line abundances measured from Magellan/MIKE follow-up spectra.}
\label{data:magellan}
\begin{tabular}{lccccc}
\multicolumn{6}{c}{J075043.12+204658.0} \\
\hline
Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/H] & [X/Fe] & $\sigma/\sqrt{N}$ \\
\hline
\ion{Fe}{I} & 82 & 6.95 & $-$0.55 &    0.00 & 0.02 \\
\ion{Mg}{I} & 3  & 7.39 & $-$0.21 & $+$0.34 & 0.13 \\
\ion{K}{I}  & 2  & 5.33 & $+$0.30 & $+$0.85 & 0.07 \\
\hline
\\
\multicolumn{6}{c}{J091825.48+172114.5} \\
\hline
Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/H] & [X/Fe] & $\sigma/\sqrt{N}$ \\
\hline
\ion{Fe}{I} & 43 & 6.51 & $-$0.99 &    0.00 & 0.03 \\
\ion{Mg}{I} & 5  & 6.56 & $-$1.04 & $-$0.05 & 0.08 \\
\ion{K}{I}  & 2  & 5.32 & $+$0.29 & $+$1.28 & 0.31 \\
\hline
\\
\multicolumn{6}{c}{J120032.60+024438.2} \\
\hline
Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/H] & [X/Fe] & $\sigma/\sqrt{N}$ \\
\hline
\ion{Fe}{I} & 77 & 6.56 & $-$0.14 & 0.00 & 0.03 \\
\ion{Mg}{I} & 4  & 6.96 & $+$0.16 & $+$0.30 & 0.09 \\
\ion{K}{I}  & 2  & 4.96 & $+$0.72 & $+$0.86 & 0.11 \\
\hline
\end{tabular}
\end{table}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{KvsMg.png}
    \caption{[K/Fe] vs [$\alpha$/Fe] for the candidate stars, overlaid with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015} as well as the three candidates observed using Magellan/MIKE (red diamonds). These three stars' abundances as per the \lamost\ spectra are indicated in the figure (red circles). Note that in principle, [$\alpha$/Fe] acts only as an upper limit for [Mg/Fe] and is used as such for our sample in this figure due to difficulties in calculating reliable [Mg/Fe] from \lamost\ data.}
    \label{KvsMg}
\end{figure}
 %See Section \ref{sec:method} for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].} 
\begin{figure}
	\includegraphics[width=\columnwidth]{KvsFe.png}
    \caption{[K/Fe] vs [Fe/H] for the candidate stars, overlaid with [K/Fe] vs [Fe/H] for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. The linear regression formula is \textrm{[K/Fe]$=-0.21 \times$[Fe/H]$+0.97$, with r$^2$=0.37}.}
    \label{KvsFe}
\end{figure}
